Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-09-14 SupportingInformation.Rmd
modified@Sept14

@@

updated on `r Sys.Date()`
\pagebreak

@@

# Nonparametric analysis of tail dependence \label{NPA}

@@

For multivariate datasets, a spatial resampling scheme was used instead of the surrogate 
approach described above.
The scheme is identical to that proposed by @bjornstadfalck2001 for application in their now 
widely used spline correlogram method; the same scheme was also used by @walteretal2017 
as part of a method for 
performing model selection among matrix regression models. For each pair of 
locations $i \neq j$, the statistic
of interest, here denoted $s_{ij}$ ($\cor_{l_b,u_b}$, $\Ps_{l_b,u_b}$, 
$\Dsq_{l_b,u_b}$, $\cor_l-\cor_u$, 
$\Ps_l-\Ps_u$, or $\Dsq_u-\Dsq_l$) was computed for those locations. The 
values $s_{ij}$ were then arranged in
a matrix, $S$, with diagonal entries NA. The mean of the non-NA entries of $S$ was computed. For 
$\cor_{l_b,u_b}$, $\Ps_{l_b,u_b}$, or $\Dsq_{l_b,u_b}$ this mean characterized the 
average strength of 
dependence, across all pairs of distinct locations, for data in the portion of the distributions 
given by $l_b$ and $u_b$. For $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, or $\Dsq_u-\Dsq_l$, the mean characterized average
asymmetry of tail dependence across all pairs of locations. 
Confidence intervals for the values of $\mean(S)$ were then computed as quantiles of a 
distribution of bootstrapped values. If $\mean(S)$ was significantly different from 0, as
revealed by these confidence intervals, for the statistics $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, 
or $\Dsq_u-\Dsq_l$, then tail dependence was significantly asymmetric, in contrast to a 
Normal null hypothesis, and answering question \hyperref[MT-Intro]{\textbf{(Q1)}} from the \nameref{MT-Intro}.
Bootstrapping was performed by resampling the locations of measurement, with replacement. 
This corresponds to 
resampling, with replacement, the rows and columns of $S$, and is described in detail elsewhere 
[@bjornstadfalck2001 ; @walteretal2017].

@@

```{r tab_soilCN_asym,echo=F,results="markup"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_soilCN_asym<-make_table_stat_fn(data=stat_soilCN_ga)
knitr::kable(tab_soilCN_asym, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption = "**Soil CN data set results** for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis. Three statistics are listed in the left column that measured asymmetry of tail dependence by comparing the distribution ranges $0-0.1$ and $0.9-1$ (see \\ref{NPA}). One thousand Kendall-preserving and 1000 Spearman-preserving surrogates with normal copula structure were created, and the same statistics were computed for the surrogates. A table entry $<N$ indicates the value of the given statistic on the data was less than its value on $N$ of the surrogates, so entries of the form $<X$ for $X$ equal to $975$ or above indicate that upper-tail dependence was significantly stronger than lower-tail dependence.\\label{tab_soilCN_asym}")
#kable_styling(, position = "float_left")
```

@@

\newpage
<!--Display model selection results for contrasts data in a table-->
```{r tab_contrasts_67fit, echo=F, results='markup'}
h<-BivMS_contrasts_67$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
knitr::kable(h,
             format='pandoc',
             caption = "Fitting info for **Anolis data set** with contrasts for AVG.ltoe.IV and AVG.humerus phylogenetic traits. \\label{tab_contrasts_67fit}",
             booktabs=T)
```

@@

<!--Display model selection results for Ceder-creek data for year 2000 in a table-->
```{r tab_cc2000fit, echo=F, results='markup'}
h<-BivMS_res_cc$`2000`$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
knitr::kable(h,
             format='pandoc',
             caption = "Fitting info for **Ceder-creek dataset** for year 2000. \\label{tab_cc2000fit}",
             booktabs=T)
```

@@

# Aphid raw data for flight duration   
#d0_flightduration<-as.matrix(read.csv("./Data/Aphid_data/APHID_DATA_RAW/aphidtsflightduration141117.csv",header=F))
```

@@

\newpage
```{r tab_ff_p_CvM, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$gfc_p_CvM,
             format='pandoc',
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for **first flight data for the leaf-curling plum aphid**. Tests were based on bootstrapping as described in Methods.\\label{tab_ff_p_CvM}",
             booktabs=TRUE
             )
```

@@

@@

Secondly, we measured 3 types of correlations (Spearman, Kendall, Pearson) and different types of non-parametric statistics (see \ref{NPA}) for both bivariate noise copula and resultant population copula for $50$ simulations. Then we plotted mean of each measured quantity with standard error against Spearman's Rho (or Kendall's Tau) of the noise copula family. Fig. \ref{fig_Cause4copula_C_spear} and Fig. \ref{fig_Cause4copula_C_kend} represent this picture for noise generating from a lower tail dependent Clayton copula whereas for Fig. \ref{fig_Cause4copula_SC_spear} and Fig. \ref{fig_Cause4copula_SC_kend} noise came from a upper tail dependent Survival Clayton family. We also carried out a paired t-test to compute the p-values of each statistic for noise and population data and found that like our first approach, here also the nature of tail dependence in noise and populations remained similar but they were not exactly the same except in Pearson correlation coefficient which ensured the Moran effect on the population data caused by environmental noise. (For code see [`Plotter_Cause4copula_stat`](https://github.com/sghosh89/BIVAN/blob/master/Cause4copula.R) function).

@@

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_count,sp=10,data_pt_thrs=30)
answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

mtext(paste0("(A) result based on kendall preserving normal surrogates, p = ",p_left),side=3,line=0.2,col="navyblue")

@@

mtext(paste0("(B) result based on spearman preserving normal surrogates , p = ",p_left),side=3,line=0.2,col="navyblue")

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10.pdf}
\caption[Skewness count for species Green spruce aphid]{Skewness count for species Green spruce aphid\label{fig_skewness_count}}
\end{center}
\end{figure}

@@

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_ff,sp=11,data_pt_thrs=30)

answer2k<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall") 
p_right<-sum(answer2k$surrogskw > answer2k$realskw)/numsurrog
mtext(paste0("(A) result based on kendall preserving normal surrogates, p = ",p_right),side=3,line=0.2,col="navyblue")

answer2s<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman") 
p_right<-sum(answer2s$surrogskw > answer2s$realskw)/numsurrog
mtext(paste0("(B) result based on spearman preserving normal surrogates , p = ",p_right),side=3,line=0.2,col="navyblue")

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11.pdf}
\caption[Skewness firstflight for species Leaf-curling plum aphid]{Skewness firstflight for species Leaf-curling plum aphid\label{fig_skewness_ff}}
\end{center}
\end{figure}

@@

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=16,data_pt_thrs=45)
answer3k<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16.pdf}
\caption[Skewness-plankton for species Ceratium furca]{Skewness-plankton for species Ceratium furca\label{fig_skewness_pns}}
\end{center}
\end{figure}

@@

pdf("./Results/skewness_results/skewness_methane/skewness_methane.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=methane_data,sp=1,data_pt_thrs=50)

answer1k<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
                           corpres="kendall") 
p_left<-sum(answer1k$surrogskw < answer1k$realskw)/numsurrog
mtext(paste0("(A) result based on kendall preserving normal surrogates, p = ",p_left),side=3,line=0.2,col="navyblue")

answer1s<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
                           corpres="spearman") 
p_left<-sum(answer1s$surrogskw < answer1s$realskw)/numsurrog
mtext(paste0("(B) result based on spearman preserving normal surrogates , p = ",p_left),side=3,line=0.2,col="navyblue")

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_methane/skewness_methane.pdf}
\caption[Skewness-methane-flux data]{Skewness-methane-flux data\label{fig_skewness_methane}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{3.4 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.1 cm} (D)} \\
\vspace{-0.5 cm} 
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_CNFSC.pdf}\\
\end{center}
\textbf{ \hspace{3.1 cm} (E) \hspace{2.4 cm} (F) \hspace{2.3 cm} (G) \hspace{2.3 cm} (H) \hspace{2.3 cm} (I)}\\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_5stats.pdf}
\caption[Spatial Taylor's Law results]{Spatial Taylor's Law results: log(spatial variance) vs. log(spatial mean) for $ns=10$ number of (A) Clayton, (B) Normal, (C) Frank, (D) Survival Clayton surrogates; (E) p-value for test of linearity, (F) p-value for test of hhomoskedasticity, (G) root mean square error, (H) intercept, (I) slope of the first panel plots. \label{fig_spTL}}
\end{center}
\end{figure}

@@

Because of overall distinct tail dependence of the multivariate copula structure, the skewness of the spatially-averaged time-series data, changed significantly from the individual skewness of time-series data. Spatial mean of the time series data extracted that tail dependence from the multivariate data set, if any, and reflected in the averaged skewness. We tested null hypothesis $H_{0}$ which presumed that multivariate copula actually came from normal copula structure with no tail dependence and thus should have the same skewness as of normal copula. So, first we generated $10000$ number of surrogate normal copula from a given multivariate copula keeping the marginal distribution and the correlation (spearman or kendall) same. Then we calculated the skewness of spatially averaged surrogate time series data, as we did with the actual multivariate data set (For code see [skewness_multivar_dataset.R](https://github.com/sghosh89/BIVAN/blob/master/skewness_multivar_dataset.R). We made a histogram of surragate skewness and found if actual skewness were within $95\%$ quantile or not. If $p$-value is less than $0.05$, then we reject the null hypothesis in support of significant tail dependence (and henceforth significantly different skewness).

>>>>

updated on `r Sys.Date()`

@@

\pagebreak

@@

<!--# Nonparametric analysis of tail dependence \label{NPA}

@@

For multivariate datasets, a spatial resampling scheme was used instead of the surrogate 
approach described above.
The scheme is identical to that proposed by @bjornstadfalck2001 for application in their now 
widely used spline correlogram method; the same scheme was also used by @walteretal2017 
as part of a method for 
performing model selection among matrix regression models. For each pair of 
locations $i \neq j$, the statistic
of interest, here denoted $s_{ij}$ ($\cor_{l_b,u_b}$, $\Ps_{l_b,u_b}$, 
$\Dsq_{l_b,u_b}$, $\cor_l-\cor_u$, 
$\Ps_l-\Ps_u$, or $\Dsq_u-\Dsq_l$) was computed for those locations. The 
values $s_{ij}$ were then arranged in
a matrix, $S$, with diagonal entries NA. The mean of the non-NA entries of $S$ was computed. For 
$\cor_{l_b,u_b}$, $\Ps_{l_b,u_b}$, or $\Dsq_{l_b,u_b}$ this mean characterized the 
average strength of 
dependence, across all pairs of distinct locations, for data in the portion of the distributions 
given by $l_b$ and $u_b$. For $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, or $\Dsq_u-\Dsq_l$, the mean characterized average
asymmetry of tail dependence across all pairs of locations. 
Confidence intervals for the values of $\mean(S)$ were then computed as quantiles of a 
distribution of bootstrapped values. If $\mean(S)$ was significantly different from 0, as
revealed by these confidence intervals, for the statistics $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, 
or $\Dsq_u-\Dsq_l$, then tail dependence was significantly asymmetric, in contrast to a 
Normal null hypothesis, and answering question \hyperref[MT-Intro]{\textbf{(Q1)}} from the \nameref{MT-Intro}.
Bootstrapping was performed by resampling the locations of measurement, with replacement. 
This corresponds to 
resampling, with replacement, the rows and columns of $S$, and is described in detail elsewhere 
[@bjornstadfalck2001 ; @walteretal2017].-->

@@

```{r tab_soilCN_asym,echo=F,results="markup"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_soilCN_asym<-make_table_stat_fn(data=stat_soilCN_ga)
knitr::kable(tab_soilCN_asym, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption = "**Soil CN data set results** for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis. Three statistics are listed in the left column that measured asymmetry of tail dependence by comparing the distribution ranges $0-0.1$ and $0.9-1$ (see \\nameref{MT-NPA}). One thousand Kendall-preserving and 1000 Spearman-preserving surrogates with normal copula structure were created, and the same statistics were computed for the surrogates. A table entry $<N$ indicates the value of the given statistic on the data was less than its value on $N$ of the surrogates, so entries of the form $<X$ for $X$ equal to $975$ or above indicate that upper-tail dependence was significantly stronger than lower-tail dependence.\\label{tab_soilCN_asym}")
#kable_styling(, position = "float_left")
```

@@

<!--Display model selection results for contrasts data in a table-->
```{r tab_contrasts_67fit, echo=F, results='markup'}
h<-BivMS_contrasts_67$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
knitr::kable(h,
             format='pandoc',
             caption = "Fitting info for **Anolis data set** with contrasts for AVG.ltoe.IV and AVG.humerus phylogenetic traits. \\label{tab_contrasts_67fit}",
             booktabs=T)
```

@@

\newpage
<!--Display model selection results for Ceder-creek data for year 2000 in a table-->
```{r tab_cc2000fit, echo=F, results='markup'}
h<-BivMS_res_cc$`2000`$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
knitr::kable(h,
             format='pandoc',
             caption = "Fitting info for **Ceder-creek dataset** for year 2000. \\label{tab_cc2000fit}",
             booktabs=T)
```

@@

# Aphid raw data for flight duration   
#d0_flightduration<-as.matrix(read.csv("./Data/Aphid_data/APHID_DATA_RAW/aphidtsflightduration141117.csv",header=F))

# Time series analysis aphids winter avg temp (here taken as -ve)
temp_aphid_raw<-as.matrix(read.csv("./Data/Aphid_data/APHID_DATA_RAW/aphidmonthlytempdata.csv",header = F))

temp_aphid<-vector("list",dim(temp_aphid_raw)[1])
names(temp_aphid)<-paste("loc",c(1:dim(temp_aphid_raw)[1]),sep="")

for(il in 1:length(temp_aphid)){

  s<-matrix(temp_aphid_raw[il,],36,12,byrow = T)
  rownames(s)<-c(1975:2010)
  colnames(s)<-c("jan","feb","mar","apr","may","jun","jul","aug","sep","oct","nov","dec")

  temp_aphid[[il]]<-s
}

winter_avg_temp<-matrix(NA,11,35)
rownames(winter_avg_temp)<-paste("loc",c(1:dim(temp_aphid_raw)[1]),sep="")
colnames(winter_avg_temp)<-c(1976:2010)

for(il in 1:length(temp_aphid)){
  temploc<-temp_aphid[[il]]
  for(i in 2:dim(temploc)[1]){
    t<-c(temploc[i-1,12],temploc[i,1:3]) # previous yr dec to present year march averaging temp.
    winter_avg_temp[il,i-1]<-mean(t,na.rm = T)
  }
}

aphid_winter_neg_temp<-vector("list",11) #initializing
names(aphid_winter_neg_temp)<-rownames(winter_avg_temp)

for(i in 1:11){
  aphid_winter_neg_temp[[i]]<-data.frame(Year=c(1976:2010),Dat=-winter_avg_temp[i,])
}

temp_aphid<-list(aphid_winter_neg_temp)
names(temp_aphid)<-"aphid_winter_neg_temp"
```

@@

```{r tab_ff_p_CvM, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$gfc_p_CvM,
             format='pandoc',
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for **first flight data for the leaf-curling plum aphid**. Tests were based on bootstrapping as described in Methods.\\label{tab_ff_p_CvM}",
             booktabs=TRUE
             )
```

@@

```{r moran_effect_on_aphid_ff, echo=F, results="hide", cache=T, cache.extra=list(seed,temp_aphid,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
set.seed(seed)
source("FittingCopula_selective_loc.R")  # top most hierarchy source file

#cat(paste("start-time: ",Sys.time(),"\n"))
RES_temp_aphid<-RES_single_sp(d_allsp=temp_aphid,sp=1,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30,
                              good_loc_given=T,good_loc=c(2:11))
#cat(paste("stop-time: ",Sys.time(),"\n")) 
resloc<-"./Results/fitting_results/"
saveRDS(RES_temp_aphid,paste(resloc,file="AphidCopulaFit_selecloc_winter_neg_temp.RDS",sep=""))

LTmUT_temp<-(RES_temp_aphid$LTdep_AICw - RES_temp_aphid$UTdep_AICw)

sum(LTmUT_temp>0,na.rm = T)
sum(LTmUT_temp<0,na.rm = T) #66 out of 90 : suggests UT in leaf-plum curling aphids firstflight data (90 out of 90 UT)
```

```{r tab_temp_aphid_bestcop, echo=F, results="markup"}
knitr::kable(RES_temp_aphid$info_ord_copname[,,1], #longtable = T,
             format='pandoc',
             #caption.short = "Best-fitting copulas for each location pair from among those considered, according to AIC, for first flight data for the leaf-curling plum aphid.",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for **negative average winter temperature data (1958-2013)**. Copulas' abbreviations were given in \\nameref{MT-Methods}. NA occurs along the diagonal of the matrix because the diagonal represents a sampling location compared to itself.  \\label{tab_temp_aphid_bestcop}",
             booktabs=TRUE
             )
```

```{r tab_temp_aphid_AICw, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$info_ord_AICw[,,1], 
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the best-fitting (lowest AIC) copula family for each location pair for **negative average winter temperature data**.\\label{tab_temp_aphid_AICw}",
             booktabs=TRUE
             )
```

```{r tab_temp_aphid_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_temp_aphid),
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for **negative average winter temperature data**, for comparison with Table \\ref{tab_ff_AICw}.\\label{tab_temp_aphid_AICw_normal}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_temp_aphid_p_CvM, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$gfc_p_CvM,
             format='pandoc',
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for **negative average winter temperature data**. Tests were based on bootstrapping as described in Methods.\\label{tab_temp_aphid_p_CvM}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_temp_aphid_p_KS, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$gfc_p_KS,
             format='pandoc',
             caption = "$P$-value results of a Kolmogorov-Smirnov-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for **negative average winter temperature data**. Tests were based on bootstrapping as described in Methods.\\label{tab_temp_aphid_p_KS}",
             booktabs=TRUE
             )
```

```{r tab_temp_aphid_LTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$LTdep_AICw,
             format='pandoc',
             caption = "Model-averaged lower tail dependence statistic for each location pair for **negative average winter temperature data**.\\label{tab_temp_aphid_LTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_temp_aphid_UTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$UTdep_AICw,
             format='pandoc',
             caption = "Model-averaged upper tail dependence statistic for each location pair for **negative average winter temperature data**.\\label{tab_temp_aphid_UTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_temp_aphid_LTmUT, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$LTdep_AICw - RES_temp_aphid$UTdep_AICw,
             digits = 5,
             format='pandoc',
             caption = "Model averaged lower tail dependence minus model averaged upper tail dependence statistic for each location pair for **negative average winter temperature data**.\\label{tab_temp_aphid_LTmUT}",
             booktabs=TRUE
             )
```

@@

Secondly, we measured 3 types of correlations (Spearman, Kendall, Pearson) and different types of non-parametric statistics (see \nameref{MT-NPA}) for both bivariate noise copula and resultant population copula for $50$ simulations. Then we plotted mean of each measured quantity with standard error against Spearman's Rho (or Kendall's Tau) of the noise copula family. Fig. \ref{fig_Cause4copula_C_spear} and Fig. \ref{fig_Cause4copula_C_kend} represent this picture for noise generating from a lower tail dependent Clayton copula whereas for Fig. \ref{fig_Cause4copula_SC_spear} and Fig. \ref{fig_Cause4copula_SC_kend} noise came from a upper tail dependent Survival Clayton family. We also carried out a paired t-test to compute the p-values of each statistic for noise and population data and found that like our first approach, here also the nature of tail dependence in noise and populations remained similar but they were not exactly the same except in Pearson correlation coefficient which ensured the Moran effect on the population data caused by environmental noise. (For code see [`Plotter_Cause4copula_stat`](https://github.com/sghosh89/BIVAN/blob/master/Cause4copula.R) function).

@@

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10.pdf",height=6,width=16)
par(mfrow=c(1,2))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_count,sp=10,data_pt_thrs=30)
answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

mtext(paste0("(A) p = ",p_left," (for Kendall preserving Normal surrogates)"),side=3,line=0.2,col="navyblue")

@@

mtext(paste0("(B) p = ",p_left," (for Spearman preserving Normal surrogates)"),side=3,line=0.2,col="navyblue")

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10.pdf}
\caption[Skewness count for species Green spruce aphid]{Skewness count for species Green spruce aphid\label{fig_skewness_count}}
\end{center}
\end{figure}

@@

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11.pdf",height=6,width=16)
par(mfrow=c(1,2))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_ff,sp=11,data_pt_thrs=30)

answer2k<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall") 
p_right<-sum(answer2k$surrogskw > answer2k$realskw)/numsurrog
mtext(paste0("(A) p = ",p_right," (for Kendall preserving Normal surrogates)"),side=3,line=0.2,col="navyblue")

answer2s<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman") 
p_right<-sum(answer2s$surrogskw > answer2s$realskw)/numsurrog
mtext(paste0("(B) p = ",p_right," (for Spearman preserving Normal surrogates)"),side=3,line=0.2,col="navyblue")

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11.pdf}
\caption[Skewness firstflight for species Leaf-curling plum aphid]{Skewness firstflight for species Leaf-curling plum aphid\label{fig_skewness_ff}}
\end{center}
\end{figure}

@@

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16.pdf",height=6,width=16)
par(mfrow=c(1,2))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=16,data_pt_thrs=45)
answer3k<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16.pdf}
\caption[Skewness-plankton for species Ceratium furca]{Skewness-plankton for species Ceratium furca\label{fig_skewness_pns}}
\end{center}
\end{figure}

@@

pdf("./Results/skewness_results/skewness_methane/skewness_methane.pdf",height=6,width=16)
par(mfrow=c(1,2))
numsurrog<-10000
loclist<-good_loclist(d_allsp=methane_data,sp=1,data_pt_thrs=50)

answer1k<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
                           corpres="kendall") 
p_left<-sum(answer1k$surrogskw < answer1k$realskw)/numsurrog
mtext(paste0("(A) p = ",p_left," (for Kendall preserving Normal surrogates)"),side=3,line=0.2,col="navyblue")

answer1s<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
                           corpres="spearman") 
p_left<-sum(answer1s$surrogskw < answer1s$realskw)/numsurrog
mtext(paste0("(B) p = ",p_left," (for Spearman preserving Normal surrogates)"),side=3,line=0.2,col="navyblue")

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/skewness_results/skewness_methane/skewness_methane.pdf}
\caption[Skewness-methane-flux data]{Skewness-methane-flux data\label{fig_skewness_methane}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{3.4 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.1 cm} (D)} \\
\vspace{-0.5 cm} 
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_CNFSC.pdf}\\
\end{center}
\textbf{ \hspace{3.1 cm} (E) \hspace{2.4 cm} (F) \hspace{2.3 cm} (G) \hspace{2.3 cm} (H) \hspace{2.3 cm} (I)}\\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=16 cm]{./Results/taylorslaw_results/SpatialTL_5stats.pdf}
\caption[Spatial Taylor's Law results]{Spatial Taylor's Law results: log(spatial variance) vs. log(spatial mean) for $ns=10$ number of (A) Clayton, (B) Normal, (C) Frank, (D) Survival Clayton surrogates; (E) p-value for test of linearity, (F) p-value for test of homoskedasticity, (G) root mean square error, (H) intercept, (I) slope of the first panel plots. \label{fig_spTL}}
\end{center}
\end{figure}

@@

Because of overall distinct tail dependence of the multivariate copula structure, the skewness of the spatially-averaged time-series data, changed significantly from the individual skewness of time-series data. To test null hypothesis $H_{0}$ which presumed that multivariate copula actually came from normal copula structure, we generated $10000$ number of surrogate normal copula from a given multivariate copula keeping the marginal distribution and the correlation (spearman or kendall) same. Then we calculated the skewness of spatially averaged surrogate time series data, as we did with the actual multivariate data set (For code see [skewness_multivar_dataset.R](https://github.com/sghosh89/BIVAN/blob/master/skewness_multivar_dataset.R). We made a histogram of surragate skewness and found if actual skewness were within $95\%$ quantile or not. If $p$-value is less than $0.05$, then we reject the null hypothesis in support of significant tail dependence (and henceforth significantly different skewness).
